Figures to insert in text

### 2018-03-02 Chapters/Chapter02.tex
sdm

Future work: classification with context using sequences --- for words instead of only letters.

We have generated a Docker image, which makes it even easier to explore the framework. After running the container, a Jupyter Notebook is available with sdm-framework and other tools already installed. The simulations run in this thesis are promptly available to be re-executed and explored. We invite the reader to take a look and explore a little bit.

>>>>

\section{Future work}

Here are some ideas that have been considered during this work, but have had to be left for future research.

\subsection{Multiple levels}

\subsection{Classification with context using sequences --- for words instead of only letters}

\subsection{Symmetrical Hard Locations}

Here is an interesting question that I leave for further research: A hypercube with n dimensions can be divided by two hypercubes with $n-1$ dimensions. Is there an algorithm that separates the area of each hard-location in such a form that there exists a function mapping each bitstring in $\{0,1\}^n$ to the set of hard locations it `belongs to'?  In other words… though this would break Kanerva's assumption of a uniformly distributed set of hard locations for a perfectly symmetrical set of hard locations, there could be large performance gains if such a mapping function from a bitstring to its corresponding set of nearest hard locations exists.

We have generated a Docker image, which makes it even easier to explore the framework. After running the container, a Jupyter Notebook is available with sdm-framework and other tools already installed. The simulations run in this thesis are promptly available to be re-executed and explored. We invite readers to take a look and explore a little bit.

### 2018-03-02 Chapters/sdm2.tex
sdm

  \subfloat[$Q_{10}$]{\includegraphics[width=4.0in]{./images02/new-images/qn10.png}}
  \caption{Here we have $Q_n$, for $n \in$ \{3, 7, 10\}. Each node represents a possible bitstring in $\{0,1\}^n$, and two nodes are linked if the bitstrings differ by a single dimension.  A number of observations can be made here. First, the number of nodes grows as $2^n$ as $n$ grows; which makes use of the entire space infeasible as $n>>20$. Another interesting observation, better seen in the figures below, is that most of the space lies at the center, at a distance of around 500 from any given vantage point. Though Kanerva has derived many combinatorial properties of the space, I believe that this is a aesthetically appealing object on its own, and beautiful results can be found in the graph-theoretical literature.\label{hypercubes}}
\end{figure}

%FOOTNOTE:
The graph composed of $\{0,1\}^n$ nodes and links between nodes $iff$ their Hamming distance is one is called the \emph{hypercube graph}, or $Q_n$.  It is a beautiful combinatorial object on its own for which one can find a survey in \citet{harary1988survey}.

Here is an interesting question that I leave for further research: A hypercube with n dimensions can be divided by two hypercubes with $n-1$ dimensions, as in Figure \ref{hypercubes}. Is there an algorithm that separates the area of each hard-location in such a form that there exists a function mapping each bitstring in $\{0,1\}^n$ to the set of hard locations it belongs to?  In other words… though this would break Kanerva's assumption of a uniformly distributed set of hard locations for a perfectly symmetrical set of hard locations, there could be large performance gains if such a mapping function from a bitstring to its corresponding set of nearest hard locations exists.

>>>>

  \subfloat[$Q_{10}$]{\includegraphics[width=4.0in]{./images02/new-images/qn10.png}}
  \caption{Here we have $Q_n$, for $n \in$ \{3, 7, 10\}. Each node represents a possible bitstring in $\{0,1\}^n$, and two nodes are linked if the bitstrings differ by a single dimension.  A number of observations can be made here. First, the number of nodes grows as $2^n$ as $n$ grows; which makes use of the entire space infeasible as $n>>20$. Another interesting observation, better seen in the figures below, is that most of the space lies at the center, at a distance of around 500 from any given vantage point.\label{hypercubes}}
\end{figure}

The graph composed of $\{0,1\}^n$ nodes and links between nodes $iff$ their Hamming distance is one is called the \emph{hypercube graph}, or $Q_n$, as in Figure \ref{hypercubes}.  Though Kanerva has derived many combinatorial properties of the space, I believe that this is a aesthetically appealing object on its own, and beautiful results can be found in the graph-theoretical literature. A good survey is found in \citet{harary1988survey}.

Here is an interesting question that I leave for further research: A hypercube with n dimensions can be divided by two hypercubes with $n-1$ dimensions. Is there an algorithm that separates the area of each hard-location in such a form that there exists a function mapping each bitstring in $\{0,1\}^n$ to the set of hard locations it belongs to?  In other words… though this would break Kanerva's assumption of a uniformly distributed set of hard locations for a perfectly symmetrical set of hard locations, there could be large performance gains if such a mapping function from a bitstring to its corresponding set of nearest hard locations exists.
